Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
new regression changes

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        school_level = s3_05a,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))

@@

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s4_01,
        register = s4_04,
        school_level = s4_05a,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur,
        depto = ID01)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2006,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy = s4_01,
        register = s4_06,
        school_level = s4_07a,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2007,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r import household data 2011}
data_2011 <- read_dta("Raw data/seminar_paper_data/2011_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_05,
        grade = s4_06b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_06a,
        urb_rur = area)

hh_2011 <- data_2011 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area,
        depto = departamento)

hh_2012 <- data_2012 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2012,
         dept = case_when(depto== "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r combine household datasets}
all_years <- hh_2005 %>% 
  #bind_rows(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)
  rbind(hh_2005, hh_2006)

@@

hh_head <- subset(total_data, relation == 1, select = c("hh_id", "sex", "age", "literacy", "dept", "urb_rur", "income", "year"))

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts"))

>>>>

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        school_level = s3_05a,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A,
        educ = aoesc,
        job = s4_16cod,
        tasks = s4_16b,
        pov_line = z,
        extr_pov = z_ext)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))

@@

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s4_01,
        register = s4_04,
        school_level = s4_05a,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur,
        depto = ID01,
        educ = añoe,
        job = s5_17cod,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2006,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy = s4_01,
        register = s4_06,
        school_level = s4_07a,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf,
        voucher = s4_05,
        educ = a_oe,
        job = s5_16co,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2007,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r import household data 2011}
data_2011 <- read_dta("Raw data/seminar_paper_data/2011_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_05,
        grade = s4_06b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_06a,
        urb_rur = area,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cod_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2011 <- data_2011 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area,
        depto = departamento,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cods5_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2012 <- data_2012 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2012,
         dept = case_when(depto== "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)

@@

hh_head <- subset(total_data, relation == 1, select = c("hh_id", "sex", "age", "literacy", "dept", "urb_rur", "income", "year", "educ", "job", "tasks", "pov_line", "extr_pov"))

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "relation", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts", "year", "job", "tasks"))

total_children <- mutate(children, id = rownames(children))

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(sex, age, literacy, educ, job, tasks, pov_line, extr_pov, hh_id) %>%
  rename (female_hhhead = sex,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)

total <- total_children %>%
  left_join(hh_head_2)

#total <- merge(children,hh_head_2, by="hh_id")

```{r creating summary statistics}

export_summary_table(dfSummary(total_children))

```{r regression variable specifications}
reg_data <- total %>%
  mutate(lny = log(income))
```

```{r regressions total sample}
install.packages("plm")
library(plm)
#example code:
#model_levels <- lm(recreation_visits ~ svr_median + svr_p10 + month_code*unit_code, data = regression_data)
#grun.fe <- plm(inv~value+capital, data = Grunfeld, model = "within")

model_simple <- plm(assist ~ floods + droughts, data = reg_data, model = "within")
summary(model_simple)
model_all <- plm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_all)
model_register <- plm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_register)
```

```{r regression rural sample}

```{r regression urban sample}
